Correlation between 16S and shotgun

### 2019-11-13 scripts/20_correlation_phylum_bw_16S_shotgun.Rmd
update

spearman_cor %>% 
  write_csv('../data/spearman_cor_phylum.csv')
```

>>>>

spearman_cor %>% 
  write_csv('../data/spearman_cor_phylum.csv')

pearson_cor <- Two %>% 
  split(.$sampleid) %>% 
  map_dfr(~ round(cor.test(.$shotgun_relab, 
                           .$s16S_relab, 
                           method = 'pearson', 
                           exact = F)$estimate, 2)) %>% 
  gather(key = 'sampleid', value = 'cor') %>% 
  arrange(cor)

pearson_cor %>% 
  write_csv('../data/pearson_cor_phylum.csv')
```

### 2019-11-13 scripts/21_correlation_genus_bw_16S_shotgun.Rmd
update

@@

py_cor %>% 
  full_join(spearman_cor %>% 
              rename(genus = rho), by = 'sampleid') %>% 
  gather(key = 'Group', value = 'Cor', names(.)[2]: names(.)[ncol(.)]) %>% 
  ggboxplot(x = 'Group', y = 'Cor',  title = 'Comparison of spearman correlation') +
  stat_compare_means() +
  ggsave('../figs/pylum_genus_correlation.jpg')
```

```{bash}
# create the shotgun table for the class order and family level
2
```

```{r}
compare_each_taxa_level <- function(){

}
```

>>>>

pearson_cor <- Two %>% 
  split(.$sampleid) %>% 
  map_dfr(~ round(cor.test(.$shotgun_relab, 
                           .$s16S_relab, 
                           method = 'pearson', 
                           exact = F)$estimate, 2)) %>% 
  gather(key = 'sampleid', value = 'cor') %>% 
  arrange(cor)

@@

py_cor %>% 
  full_join(spearman_cor %>% 
              rename(genus = rho), by = 'sampleid') %>% 
  gather(key = 'Group', value = 'Cor', names(.)[2]: names(.)[ncol(.)]) %>% 
  ggboxplot(x = 'Group', y = 'Cor',  title = 'Comparison of spearman correlation') +
  stat_compare_means() +
  ggsave('../figs/pylum_genus_correlation.jpg')

```{r}
py_cor <- read_csv('../data/pearson_cor_phylum.csv') %>% 
  rename(pylum = cor)

py_cor %>% 
  full_join(pearson_cor %>% 
              rename(genus = cor), by = 'sampleid') %>% 
  gather(key = 'Group', value = 'Cor', names(.)[2]: names(.)[ncol(.)]) %>% 
  ggboxplot(x = 'Group', y = 'Cor',  title = 'Comparison of Pearson correlation') +
  stat_compare_means() +
  ggsave('../figs/pylum_genus_correlation_pearson.jpg')
```
